% BEÁLLÍTÁSOK - JOBB NEM VÁLTOZTATNI
\documentclass[final]{ubb_dolgozat}
\usepackage{definitions}
%%


% milyen nyelveken akarunk forráskódot megjeleníteni
\lstloadlanguages{java,scala}

% ezt be lehet tenni MINDEGYIK megjelenítendõ kód elé.
\lstset{language=scala}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%!!          EZT KELL VÁLTOZTATNI       !!%%%%
%%     A DOLGOZAT CÍMOLDALÁNAK ELEMEI        %%

%% MELYIK ÉVBEN ADJUK LE
\submityear{%
2014
}
%% MELYIK HÓNAPBAN ADJUK LE
\submitmonthHU{%
Július
}
\submitmonthRO{%
Iulie
}
\submitmonthEN{%
July
}

\titleHU{%
Egy Ügyes Vizsgadolgozat
}

% Amennyiben szükséges, az alábbi sorokat ki kell komment-ezni és 
% beírni a megfelelõ címeket

\titleEN{%
  FEST-Logging
}

\titleRO{%
  FEST-Logging
}

\author{%
Zsolt Donca
}

%%
\tutorHU{%
dr. Csató Lehel, egyetemi docens\\
%{\large Babe\c{s}--Bolyai Tudományegyetem,\\
% Matematika és Informatika Kar}% ha különbözik, akkor fel kell tûntetni
}
%%
\tutorRO{%
Conf. dr, Lehel Csató\\
% {\large Universitatea Babe\c{s}--Bolyai,\\ % dacã diferã!!!
% Facultatea de Matematic\u{a} \c{s}i Informatic\u{a} }%
}
%%
\tutorEN{%
Assoc. prof. dr. Lehel Csató
% {\large Babe\c{s}--Bolyai University,\\
% Faculty of Mathematics and Informatics}
}



%\usepackage{t1enc}
%\usepackage{ucs}
%\usepackage[utf8x]{inputenc}

%\usepackage[pdftex]{graphicx}
%\usepackage{url}
%\usepackage{algorithmic}
%\usepackage{amsmath}
%\usepackage{amssymb}

%\usepackage[table]{xcolor}
%\usepackage{listings}
%\usepackage[colorlinks=true]{hyperref}
\newcommand*{\fullref}[1]{\hyperref[{#1}]{\autoref*{#1} \nameref*{#1}}} % One single link

\lstdefinelanguage{scala}{
  morekeywords={abstract,case,catch,class,def,%
    do,else,extends,false,final,finally,%
    for,if,implicit,import,match,mixin,%
    new,null,object,override,package,%
    private,protected,requires,return,sealed,%
    super,this,throw,trait,true,try,%
    type,val,var,while,with,yield},
  otherkeywords={=>,<-,<\%,<:,>:,\#,@},
  sensitive=true,
  morecomment=[l]{//},
  morecomment=[n]{/*}{*/},
  morestring=[b]",
  morestring=[b]',
  morestring=[b]"""
}

\usepackage{parskip}

\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
 
% Default settings for code listings
\lstset{%frame=tb,
  language=scala,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
%  frame=single,
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}



%\setcounter{secnumdepth}{3}
%\setcounter{tocdepth}{3}

% experimentary tabular stuff

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}



\begin{document}

%% ABSTRAKT
\begin{abstractEN} % ANGOL VÁLTOZAT

% a lenti részt értelemszerûen ki kell tölteni a dolgozat angol kivonatával.
% A BEGIN ... END között CSAK A SAJÁT SZÖVEG kell, hogy legyen.
% Az utolsó mondatot benne kell hagyni, mely által kijelentitek, hogy a munkátok SAJÁT.


{ \color{gray!60!red}
	FEST-Logging an extension for the functional GUI testing system FEST-Swing that tests Swing based desktop Java applications or applets. FEST-Logging logs execution details of test suites, helping development, troubleshooting or optimization efforts, easily integrating into existing test systems requiring few code changes.

FEST-Logging is demonstrated with a simple file manager application developed in the functional programming language \emph{Scala}. The application was developed using the library \emph{Scala.React} as a proof-of-concept of the article \emph{Deprecating the Observer Pattern with Scala.React}\cite{DeprecatingObservers}.

	\vfill
  
}

This work is the result of my own activity. I have neither given nor received unauthorized assistance on this work.

\end{abstractEN}


\maketitle

{ \baselineskip 1ex
  \parskip 1ex
  \tableofcontents
}


\include{f_introduction}
\include{f_theory}
\include{f_implementation}

\appendix
\include{f_examples}


{ \renewcommand{\baselinestretch}{0.8}\normalsize %
  \setlength{\itemsep}{-2.4mm}
  \setlength{\bibspacing}{0.67\baselineskip}
  \bibliographystyle{abbrvnat}
  \bibliography{paper_bibliography}
}


\end{document}
